Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Additional clarification

\comment{\textit{I did change the lineup scoring - for some reason, I was averaging before (and I hadn't included the third battery of lineups b/c of scoring issues).}}

>>>>

\comment{\textit{I did change the lineup scoring - for some reason, I was averaging before (and I hadn't included the third battery of lineups b/c of scoring issues). That explains the scale, but not the change in art skills association.}}
